\batcave: Calling somatic mutations with a tumor- and site-specific prior

### 2019-12-20 NAR_DRAFT.tex
add table for shi et al. needs mutation rates when they finish

\subsection{Real data}
We analyzed two real data sets, one from an acute myeloid leukemia (AML)~\cite{Griffith2015} and one from a multi-region sequencing experiment in breast cancer~\cite{Shi2018}.
We downloaded the normal and primary whole-genome AML tumor bam files from dbGaP accession number phs000159.v8.p4.
Griffith et al.\ generated a platinum set of variant calls for this tumor~\cite{Griffith2015}, which we used for our true positive dataset.
We downloaded the normal and tumor whole-exome breast cancer bam files from NCBI Sequence Read Archive accession SRP070662.
\rngcomment{Griffith et al.\ estimated the purity of their primary sample to be 90.7\%, and we used this value for tumor purity in \texttt{batcaver}.}
Shi et al.\ generated a gold set of variant calls for each tumor region sequenced~\cite{Shi2018}, which we used for our true positive dataset.
For these multi-region data, we \rngcomment{used the XXX samples} and ran \batcave separately on each sequenced region and combined results to generate precision-recall curves.
\rngcomment{Shi et al.\ estimated sample purities of between XXX and XXX, so we set the purities each sample to XXX.}
We called variants using Mutect 1.1.7 as in our simulations, except that both these data sets were originally aligned to GRCrh37, so we used that reference.

@@

>>>>

\subsection{Real data}
We analyzed two real data sets, one from an acute myeloid leukemia (AML)~\cite{Griffith2015} and one from a multi-region sequencing experiment in breast cancer~\cite{Shi2018}.
We downloaded the normal and primary whole-genome AML tumor bam files from dbGaP accession number phs000159.v8.p4.
Griffith et al.\ generated a platinum set of variant calls for this tumor~\cite{Griffith2015}, which we used for our true positive dataset.
We downloaded the normal and tumor whole-exome breast cancer bam files from NCBI Sequence Read Archive accession SRP070662.
\rngcomment{Griffith et al.\ estimated the purity of their primary sample to be 90.7\%, and we used this value for tumor purity in \texttt{batcaver}.}
Shi et al.\ generated a gold set of variant calls for each tumor region sequenced~\cite{Shi2018}, which we used for our true positive dataset.
For these multi-region data, we analyzed the three biological replicates from each of six tumors, running \batcave separately on each of the eighteen, and combined results to generate precision-recall curves.
\rngcomment{Shi et al.\ estimated sample purities of between XXX and XXX, so we set the purities each sample to XXX.}
We called variants using Mutect 1.1.7 as in our simulations, except that both these data sets were originally aligned to GRCrh37, so we used that reference.

@@

\section{Supplementary tables}

\begin{table*}[b]
  \tableparts{%
  \caption{Sample summary for Shi et al.}
  \label{table:01}%
  }{%
  \begin{tabular}{lll}
  \toprule
  Sample & Purity estimate (\%) & Mutation rate estimate 
  \\
  \colrule
  Case 1 biorep A & 53.8 & 3.6e-7 
  \\
  Case 1 biorep B & 46.3 & 3.2e-7 
  \\
  Case 1 biorep C & 26.0 & 3.2e-7 
  \\
  Case 2 biorep A & 40.0 & 3.6e-7 
  \\
  Case 2 biorep B & 32.3 & 3.6e-7 
  \\
  Case 2 biorep C & .4(*) & 3.6e-7 & 
  \\
  Case 3 biorep A & 56.4 & 3.6e-8 
  \\
  Case 3 biorep B & 72.8 & 7e-7 
  \\
  Case 3 biorep C & 64.9 & 7e-7 
  \\
  Case 4 biorep A & 60.4 & 7e-7 
  \\
  Case 4 biorep B & 61.7 & 7e-7 
  \\
  Case 4 biorep C & 57.6 & 7e-7 
  \\
  Case 5 biorep A & 78.7 & 7e-7 
  \\
  Case 5 biorep B & 76.7 & 7e-7 
  \\
  Case 5 biorep C & 80.8 & 7e-7 
  \\
  Case 6 biorep A & 47.8 & 7e-7 
  \\
  Case 6 biorep B & 49.4 & 7e-7 
  \\
  Case 6 biorep C & 52.9 & 7e-7 
  \\
  \botrule
  \end{tabular}%
  }
  {Shi et al. did not provide an estimate of purity for Case 2 biorep C. We chose .4 because it is similar to the other biological replicates from this sample.}
\end{table*}
